Interactive Filter and Display of Hillary Clinton's Emails: \\A Cautionary Tale of Metadata

### 2017-04-02 VAST_submission/vgtc_journal_latex/paper.tex
changed back to ten patches; Dec 2012 treated as two (as originally)

Following this approach, nine %ten 
more patches can be found (in addition to that of Section~\ref{sect:emailGap}).  With the dates in hand, an internet search can be conducted to see what, if anything, might turn up to explain the patch.
%\subsubsection{You have no mail \ldots}
\subsubsection{Early days}
\label{sect:youHaveNoMail}
The first, and largest, patch occurs at the very beginning of Clinton's tenure as Secretary of State.  It is  obvious even from the full time series of Figure~\ref{fig:VolumeAll}.  Essentially no email from Secretary Clinton, and little from anyone else appears until mid to late April 2009.

@@

\subsubsection{December 2012}
The last patch appears 
shortly after the email gap from Section~\ref{sect:emailGap}.  Figure~\ref{fig:ZeroEmailsDec2012}
\begin{figure}[h]
\begin{center}
\includegraphics[width=0.95\linewidth]{ZeroEmailsDec2012}
\caption{Dec 3 -- Jan 14, 2012:  Selected Emails are from Clinton; Scheduled foreign travel marked in blue.}
\label{fig:ZeroEmailsDec2012}
\end{center}
\end{figure}
shows two closely related gaps in December 2012 which, for the purposes of discourse only,  we are counting as only one of our 
%ten 
nine
patches.  Similar to June 2009, there is an easy explanation at hand.  Clinton had suffered a concussion ``\ldots in a fall brought on by an illness'' \cite{concussion} and was recovering at home by December 15.  She had `already been forced to cancel a planned trip to the Middle East and north Africa'' \cite{concussion} that week; this is not the foreign travel shown in Figure~\ref{fig:ZeroEmailsDec2012} \cite{ForeignSched}.

>>>>

Following this approach, ten 
more patches can be found (in addition to that of Section~\ref{sect:emailGap}).  With the dates in hand, an internet search can be conducted to see what, if anything, might turn up to explain the patch.
%\subsubsection{You have no mail \ldots}
\subsubsection{Early days}
\label{sect:youHaveNoMail}
The first, and largest, patch occurs at the very beginning of Clinton's tenure as Secretary of State.  It is  obvious even from the full time series of Figure~\ref{fig:VolumeAll}.  Essentially no email from Secretary Clinton, and little from anyone else appears until mid to late April 2009.

@@

\subsubsection{Two patches in December 2012}
The last two patches appear 
shortly after the email gap from Section~\ref{sect:emailGap}.  As seen in Figure~\ref{fig:ZeroEmailsDec2012}
\begin{figure}[h]
\begin{center}
\includegraphics[width=0.95\linewidth]{ZeroEmailsDec2012}
\caption{Dec 3 -- Jan 14, 2012:  Selected Emails are from Clinton; Scheduled foreign travel marked in blue.}
\label{fig:ZeroEmailsDec2012}
\end{center}
\end{figure}
these are the two closely related gaps in December 2012 which,
% for the purposes of discourse only,  we are counting as only one of our 
%ten patches
might be counted as one large gap.
Similar to June 2009, there is an easy explanation at hand, at least for the first of these.  Clinton had suffered a concussion ``\ldots in a fall brought on by an illness'' \cite{concussion} and was recovering at home by December 15.  She had `already been forced to cancel a planned trip to the Middle East and north Africa'' \cite{concussion} that week; this is not the foreign travel shown in Figure~\ref{fig:ZeroEmailsDec2012} \cite{ForeignSched}.
